\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[T1]{fontenc}
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.55in}
\addtolength{\textheight}{1.1in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\centering\scshape
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

%-------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

\newcommand{\resumeSkillHeading}[1]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l}
      \textbf{#1} \\
    \end{tabular*}\vspace{-5pt}
}

%-------------------- START DOCUMENT --------------------
\begin{document}

%----------- HEADING -----------
\begin{center}
    {\LARGE Neil Tripathi} \\ \vspace{2pt}
    San Francisco, CA \,|\, (929) 476-5255 \,|\, \href{mailto:neiltripathi93@gmail.com}{neiltripathi93@gmail.com} \\
    \href{https://github.com/neilt93}{github.com/neilt93}
    \,|\, \href{https://neiltripathi.com}{neiltripathi.com} \,|\,
    \href{https://www.linkedin.com/in/neil-tripathi-001b50300/}{linkedin.com/in/neil-tripathi-001b50300} \\
\end{center}

%----------- EDUCATION -----------
\section{Education}
\resumeSubHeadingListStart

  \resumeSubheading
    {New York University}{Sep 2022 -- Dec 2025}
    {B.A. Computer Science, Minor: Mathematics, GPA: 3.77/4.00}{New York, NY}
  \resumeItemListStart
    \resumeItem{Dean's List (2023--2024, 2024--2025). Coursework: ML, AI, NLP, algorithms, operating systems, cryptography, databases.}
  \resumeItemListEnd

  \resumeSubheading
    {St Olave's Grammar School}{Sep 2016 -- Jun 2022}
    {A levels: Mathematics, Further Mathematics, Computer Science, Physics (A* in each)}{London, UK}

\resumeSubHeadingListEnd

%----------- RESEARCH & PUBLICATIONS -----------
\section{Research \& Publications}
\resumeSubHeadingListStart

  \resumeSubheading
    {TAP-Score: Runtime Failure Detection for Diffusion Policy}{Jan 2026 -- Present}
    {Independent Research}{}
  \resumeItemListStart
    \resumeItem{Trained a supervised risk predictor on real visuomotor rollouts to detect when a Diffusion Policy will fail before execution completes.}
    \resumeItem{Achieved AUROC 0.972 on Can and 0.982 (obs-only) on Lift under zero-object perturbation; selective execution yields 100\% success at 20\% coverage vs 45\% baseline.}
    \resumeItem{Built a world-model guardrail (action-conditioned latent model, success-only training); fusion of WM + TAP reaches AUROC 0.923.}
  \resumeItemListEnd

  \resumeSubheading
    {Temporal Reasoning Benchmark for Large Language Models}{Mar 2026 -- Present}
    {Independent Research}{}
  \resumeItemListStart
    \resumeItem{Built a benchmark testing whether LLMs recognise when their context is stale; fine-tuned GPT-2 and TinyLlama with time-conditioned inputs.}
    \resumeItem{Frontier eval: GPT-5.4 shows 100\% false trust without timestamps, 0\% with; Claude Opus reaches 100\% switch sensitivity. Key finding: more capable models are more confidently wrong when timestamps are absent.}
  \resumeItemListEnd

  \resumeSubheading
    {Benchmarking Commonsense Visual Reasoning for Vision-Language Models}{2025 -- 2026}
    {Co-author with Prof. Ernest Davis (NYU); arXiv cs.AI, Mar 2026}{}
  \resumeItemListStart
    \resumeItem{Designed a visibility-reasoning benchmark (100 families, 300 headline cells, 2$\times$2 XOR design) with automated graders and scoring.}
    \resumeItem{Evaluated 9 VLMs across three tiers (flagship, prior-gen, open-source); surfaced a 26\% abstention rate in GPT-5 as key finding.}
  \resumeItemListEnd

  \resumeSubheading
    {Adversarial Robustness of 3D U-Net Radiation Therapy Dose Prediction}{2025 -- 2026}
    {Co-author; accepted at SERA 2026 (IEEE/ACIS); submitted to ASTRO 2026}{}
  \resumeItemListStart
    \resumeItem{Evaluated adversarial (FGSM/PGD) and clinically plausible CT perturbations on the OpenKBP dataset using DVH metrics; identified resolution downsampling as the only perturbation with immediate clinical impact.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%----------- EXPERIENCE -----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Cybernetic AI}{Mar 2026 -- Present}
    {Research Engineer, Robotics}{San Francisco, CA (Remote)}
  \resumeItemListStart
    \resumeItem{Built FIPER + Sentinel runtime failure diagnostics for the RoboEval platform: paper-accurate implementations of STAC conformal prediction, RND-OE on observation embeddings, and ACE (Action Chunk Entropy) for diffusion policies.}
    \resumeItem{Shipped sim-to-real pipeline for SO-101 packing and Franka pick-and-place: 2-camera SmolVLA deployment, GR00T N1.6 policy integration, Isaac Sim episode generator, and joint-space bridge from simulation to real hardware.}
    \resumeItem{Added VLM-based task progress signal (Qwen2.5-VL-7B host-side scoring) and Sentinel combined-alarm logic; resolved 20+ PR review issues and a full production audit (3 critical, 7 medium, 7 low).}
  \resumeItemListEnd

  \resumeSubheading
    {Sentient Labs}{May 2025 -- Aug 2025}
    {AI Product \& Research Intern}{New York City, NY (Hybrid)}
  \resumeItemListStart
    \resumeItem{Built an internal evaluation suite of 100+ LLM prompts with automated scoring for tool-call correctness and safety-violation rate.}
    \resumeItem{Improved feedback-to-ticket latency by ~20\% via regression harness and iteration notes; shipped 3 tool integrations with engineers.}
    \resumeItem{Built a real-time crypto signals dashboard (2--3k lines backend TS, ~1k lines frontend React) with latency under 2s for exchange data.}
    \resumeItem{Prototyped 'Dobby Mode' agent (300-line Streamlit demo) using Dolphin Mistral; enforced JSON schema to reduce hallucinations.}
  \resumeItemListEnd

  \resumeSubheading
    {New York University}{Jan 2025 -- May 2025}
    {Teaching Assistant, Database Design}{New York City, NY}
  \resumeItemListStart
    \resumeItem{Led recitations on SQL, MongoDB, Flask/Jinja, and schema design; supported 50+ students via office hours and grading.}
  \resumeItemListEnd

  \resumeSubheading
    {4mainstreet.ai}{May 2024 -- Aug 2024}
    {ML and Full-Stack Intern}{Fremont, CA (Remote)}
  \resumeItemListStart
    \resumeItem{Built data pipelines for customer voice + text (4,000 records); integrated outputs into a Flutter front-end.}
    \resumeItem{Built an evaluation harness to benchmark Llama 3 8B, Gemini, and GPT-class models on 4,000 labeled examples; computed precision/recall/F1 and surfaced failure modes to guide model selection.}
  \resumeItemListEnd

  \resumeSubheading
    {Scroll.io}{May 2023 -- Aug 2023}
    {Software Engineering Intern (Blockchain and Data)}{New York City, NY (Remote)}
  \resumeItemListStart
    \resumeItem{Built a Discord analytics tool for a 20K+ community; automated ingestion into BigQuery and cut manual reporting by 5 hours/week.}
  \resumeItemListEnd

\resumeSubHeadingListEnd


%----------- PROJECTS -----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeSubheading{Physical.AI: Data-Driven Marketplace for Physical Ads}{Jan 2025 -- Present}{Co-Founder}{San Francisco, CA}
  \resumeItemListStart
    \resumeItem{Built Zillow-style discovery experience for physical ads on a map; achieved top 6 at YC W25 hackathon finals out of 100+ teams.}
    \resumeItem{Integrated live \textit{attention score} using Caltrans PeMS traffic data to estimate OTS volume, dwell time, and impact by time of day.}
    \resumeItem{Backend ingests ad placements, maps to nearby sensors, computes metrics against historical baselines, and surfaces ticker-style scores.}
  \resumeItemListEnd
  \resumeSubheading{Sympli, Voice-First Health Companion App}{Aug 2025 -- Present}{Technical Co-Founder}{New York, NY}
  \resumeItemListStart
    \resumeItem{Built voice intake $\rightarrow$ clinician-style note pipeline (ASR + summarization) with latency under 1 minute; added end-to-end instrumentation.}
    \resumeItem{Deployed HIPAA-aware AWS stack (TypeScript + Postgres + self-hosted LLM); shipped an alpha to 20 users (100+ sessions).}
  \resumeItemListEnd

  \resumeSubheading
    {Connectome-Driven Locomotion Controller}{Mar 2026 -- Present}
    {Independent Research}{}
  \resumeItemListStart
    \resumeItem{Simulated the MANC ventral nerve cord (13,101 neurons, 1.9M synapses) in Brian2 with FlyGym v2; built a proprioceptive encoder from BANC sensory pathways and a structural descent optimiser for connectome-guided gradient projection.}
    \resumeItem{Demonstrated emergent odor avoidance from connectome wiring alone (no engineered navigation logic) and discovered a 2-neuron hygrosensory bottleneck (DNb05).}
    \resumeItem{Deploying to a Waveshare HexArth hexapod (18-DOF Dynamixel servos) with serial protocol bridge for closed-loop sim-to-real transfer.}
  \resumeItemListEnd

  \resumeSubheading
    {Prediction Market Forecasting Agent}{Mar 2026 -- Present}
    {Independent Project}{}
  \resumeItemListStart
    \resumeItem{Built a local-first forecasting agent with LLM-driven sub-question decomposition, devil's advocate debate, and LightGBM calibration for automated Kalshi trading.}
    \resumeItem{Backtested across 229 markets with Qwen 14B: 80\% directional accuracy, Brier score 0.0033; dynamic ECE thresholds for position sizing.}
  \resumeItemListEnd

  \resumeSubheading
    {Crypto Safety Wallet: LLM-Native Wallet with Adversarial Safety Engine}{2026 -- Present}
    {Independent Project}{}
  \resumeItemListStart
    \resumeItem{Built a natural-language wallet on Base with 11 intent types (send, swap, batch, chain, streaming, bridging) plus a 4-check safety pipeline covering simulation, approval scope, reputation, and semantic review.}
    \resumeItem{Designed a 170-case eval suite including 32 adversarial tests across 6 attack categories (prompt-injection, address-poisoning, approval-exploit, social-engineering, amount-manipulation, phishing).}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%----------- TECHNICAL SKILLS -----------
\section{Technical Skills}
\resumeSubHeadingListStart

  \resumeSkillHeading{Languages}
  \resumeItemListStart
    \resumeItem{Python, TypeScript, SQL, Java, Rust, C}
  \resumeItemListEnd

  \resumeSkillHeading{Machine Learning}
  \resumeItemListStart
    \resumeItem{PyTorch, TensorFlow, MuJoCo, FlyGym, Brian2, diffusion models, world models, PPO, LLM fine-tuning, evaluation pipelines, agent tool use}
  \resumeItemListEnd

  \resumeSkillHeading{Data \& Cloud}
  \resumeItemListStart
    \resumeItem{Postgres, MongoDB, BigQuery, Supabase, AWS, RunPod, Docker, Next.js, FastAPI, Vercel}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%----------- LANGUAGES -----------
\section{Languages}
\resumeItemListStart
  \resumeItem{English (fluent), Hindi (fluent), Spanish (intermediate), French (basic)}
\resumeItemListEnd

%----------- OTHER INTERESTS -----------
\section{Other Interests}
\resumeItemListStart
  \resumeItem{Competitive gaming (usually top ~2,000 globally in \textit{Clash Royale}, Grand Champion III in \textit{Rocket League}, peaked at rank 598 in \textit{Marvel Rivals}), the gym, and sports like football, rugby, badminton, table tennis, and fives.}
\resumeItemListEnd

\end{document}
